### 2016-09-30 architecture.tex
Make it clear that SymEngine is not used in SymPy 1.0

SymPy has recently started to use SymEngine as an
optional backend, initially in \texttt{sympy.\allowbreak{}physics.\allowbreak{}mechanics} only.
Future work will involve
allowing more algorithms in SymPy to use SymEngine as a backend.

>>>>

The development branch SymPy has recently started to use SymEngine as an
optional backend, initially in \texttt{sympy.\allowbreak{}physics.\allowbreak{}mechanics} only.
Future work will involve
allowing more algorithms in SymPy to use SymEngine as a backend.
